Paper: Convex Covering

### 2024-01-05 els2024-convex-covering/paper.tex
Cite MPR

\section{Introduction}\label{introduction}
Many geometrical applications such as games require efficient intersection tests between various geometrical shapes. Efficient algorithms for such intersection tests such as GJK\cite{gilbert1988fast} require the involved shapes to be convex, however. This is a difficult constraint, as most shapes encountered in nature and in environments designed for games are non-convex. A simple solution to this problem is to compute a convex-hull over the concave shape. However, this creates imprecision in the collision result, which may not always be permissible. Especially for highly non-convex objects such as terrain or building interiors, merely computing a convex-hull is not feasible.
Instead, we need to decompose the shape into multiple convex shapes.

Since computing an optimal convex decomposition is NP-hard\cite{1056648} all algorithms to perform such decompositions operate on heuristics and various relaxations of the constraints. A frequent relaxation is to allow the resulting shapes to be ``approximately convex''. This is usually permissible as the intersection test algorithms still deliver results that are accurate enough even in the presence of very small concavities. Another relaxation is to allow the convex hulls to not have to match the input surface exactly. However, for the case of environment geometry in games, this approximation means that the resulting shapes can produce geometry that leads to collisions that would not be present if a test were performed against the input mesh instead. Such protrusions and inaccuracies can be significant enough to be noticeable to the player.

>>>>

\section{Introduction}\label{introduction}
Many geometrical applications such as games require efficient intersection tests between various geometrical shapes. Efficient algorithms for such intersection tests such as GJK\cite{gilbert1988fast} or MPR\cite{snethen2008xenocollide} require the involved shapes to be convex, however. This is a difficult constraint, as most shapes encountered in nature and in environments designed for games are non-convex. A simple solution to this problem is to compute a convex-hull over the concave shape. However, this creates imprecision in the collision result, which may not always be permissible. Especially for highly non-convex objects such as terrain or building interiors, merely computing a convex-hull is not feasible.
Instead, we need to decompose the shape into multiple convex shapes.

Since computing an optimal convex decomposition is NP-hard\cite{1056648} all used algorithms to perform such decompositions operate on heuristics and various relaxations of the constraints. A frequent relaxation is to allow the resulting shapes to be ``approximately convex''. This is usually permissible as the intersection test algorithms still deliver results that are accurate enough even in the presence of very small concavities. Another relaxation is to allow the convex hulls to not have to match the input surface exactly. However, for the case of environment geometry in games, this approximation means that the resulting shapes can produce geometry that leads to collisions that would not be present if a test were performed against the input mesh instead. Such protrusions and inaccuracies can be significant enough to be noticeable to the player.
